Solve LMI with saturation 1 dimensional case

### 2024-10-22 Linear integrator 1 dimension case/ideas.tex
Folder order

\documentclass{article}
\input{math_commands}
\input{custom_imports}
\usepackage[margin=54pt]{geometry}
\usepackage{biblatex}
\addbibresource{biblio.bib}

@@

\subsection*{Scalar approach}
Follow the approach used in paper \cite{isabelle-paper} to find out how they dealt with $\gamma \bar{\nu}^{2} = \tau$ with \texttt{fminsearch}

>>>>

\documentclass{article}
\input{../math_commands}
\input{../custom_imports}
\usepackage[margin=54pt]{geometry}
\usepackage{biblatex}
\addbibresource{../biblio.bib}

@@

The ellipsoid condition without bilinear terms is:

\begin{equation}
  \bmx{
    P & G\tr \\
    G & \gamma \bar{\nu}^{2}
  } \geq 0
\end{equation}

The problem that arises now is that imposing $G = -K - T^{-1} B\tr P A_k$ results in a bilinear condition since we have both $T^{-1}$ and $P$

\subsection*{Scalar approach}

Follow the approach used in paper \cite{isabelle-paper} to find out how they dealt with $\gamma \bar{\nu}^{2} = \tau$ with \texttt{fminsearch}

\textbf{Paper analysis}: \dots Interrupted immediately since I found a value for $\alpha$ with respect to equation \ref{ellipsoid} and paper \cite{css-extended}: $\alpha = 1$\dots

\section*{Pendulum with integrator}
Since I found the solution for the LMI for the case without integrator, I can now try to solve the case with integrator. The plant is now:

\begin{equation}
  \bmx{
  \theta \\
  \dot{\theta} \\
  \eta
  }^{+} = \bmx{
  1 & \delta t & 0\\
  \frac{g}{l} dt & 1 - \frac{\mu}{m l^2} dt & 0\\
  1 & 0 & 1
  } \bmx{
  \theta \\
  \dot{\theta} \\
  \eta
  } + \bmx{
    0 \\
    \frac{dt}{m l^2} \\
    0
  } u = A x + B u
\end{equation}

Following analogous considerations I end up with a condition formally identical as in equation. \ref{matricione}. The only difference is that the dimensions of the matrices that now are scaled accordingly and the gain matrix $K$ that is now the proper LQR gain for the new system with integrator. I set up the ellipsoid condition as in equation \ref{ellipsoid} with $\gamma = 1$. Introducing the variable $Z = TG$ and exploiting the result from:

$$
  \left[ \bar{\nu}^{-2} - T \right] \bar{\nu}^{2} \left[ \bar{\nu}^{-2} - T \right] \geq 0 \to \bar{\nu}^{-2} - T - T + \bar{\nu}^{2} T^{2} \geq 0 \to \bar{\nu}^{2} T^{2} \geq 2 T - \bar{\nu}^{-2}
$$

Equation. \ref{ellipsoid} becomes:

\begin{equation}
  \bmx{
    P & Z\tr \\
    Z & 2 T - \bar{\nu}^{-2} 
  } \geq 0
\end{equation}

That guarantees the validity in a local region of the state space. Specifically the region defined by the ellipsoid $\cE(P, x_*) = \left\{ x \in \RR^{n_{F}} : (x - x_*)\tr P (x - x_*) \leq 1 \right\}$ that is represented in the following plots.

\begin{figure}[H]
    \centering
    \begin{subfigure}{0.48\textwidth}
    \includegraphics[width=\textwidth]{img/red_state_out}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.48\textwidth}
    \includegraphics[width=\textwidth]{img/lyap_out}
    \end{subfigure}
    \caption{Initial state out of ROA, the system is still able to reach the origin but the Lyapunov function is not strictly decreasing}
\end{figure}

\begin{figure}[H]
    \centering
    \begin{subfigure}{0.48\textwidth}
    \includegraphics[width=\textwidth]{img/red_state_inside}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.48\textwidth}
    \includegraphics[width=\textwidth]{img/lyap_inside}
    \end{subfigure}
    \caption{Initial state inside the ROA, the system is able to reach the origin and the Lyapunov function is strictly decreasing}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.5\textwidth]{img/detail_lyap}
    \caption{Detail of the Lyapunov function in the case the initial state is inside the ROA}
\end{figure}

\subsection*{Next steps}
Now the following steps regard the extraction of the "region of linearity" from this trivial 1 layer case and extend it iteratively to craft a multi-layer network controller by hand.
